
---
title: "Simple document"
output: github_document
  toc: true 
  toc_float: true #table of contents 
---

Notes from lecture: 
```{r}
#example_df$vec_numberic #DN you this structure, use below 
#pull(example_df, vec_numeric) #better structure 
```

I'm an R Markdown document! 

# Section 1

Here's a **code chunk** that samples from 
a _normal distribution_:

```{r}
library(tidyverse)
samp = rnorm(100)
length(samp)
```

# Section 2

I can take the mean of the sample, too!

eval = FALSE: code will be displayed but not executed; results are not included.
echo = FALSE: code will be executed but not displayed; results are included.
include = FALSE: code will be executed but not displayed; results are not included.
message = FALSE and warning = FALSE: prevents messages and warnings from being displayed.
results = hide and fig.show = hide: prevents results and figures from being shown, respectively.
collapse = TRUE: output will be collapsed into a single block at shown at the end of the chunk.
error: errors in code will stop rendering when FALSE; errors in code will be printed in the doc when TRUE. The default is FALSE and you should almost never change it.

```{r generate_plot, echo = FALSE}
plot_df = tibble(
  x = rnorm(1000, sd = .5),
  y = 1 + 2 * x + rnorm(1000)
)
```

the number of rows in `plot_df` is `r nrow(plot_df)`. ***



control+option + I <- hot keys for inserting new code chunk 
```{r}

```

Write a named code chunk that creates a dataframe comprised of: a numeric variable containing a random sample of size 500 from a normal variable with mean 1; a logical vector indicating whether each sampled value is greater than zero; and a numeric vector containing the absolute value of each element. Then, produce a histogram of the absolute value variable just created. Add an inline summary giving the median value rounded to two decimal places. What happens if you set eval = FALSE to the code chunk? What about  echo = FALSE?

```{r}
df <- tibble(
  num_var = rnorm(500, mean = 1), 
  binary_var = num_var > 0, # binary_var  = ifelse(num_var > 0, 1, 0), 
  num_var2 = abs(num_var)
)
ggplot( df, aes(x = num_var2)) + geom_histogram()

median_samp = median(pull(df, num_var))

```

Inline summary: 

The median of the sample is `r round(median_samp, digits = 2)`. 


Tables 
------------------------------------------------------------

First Header  | Second Header
------------- | -------------
Content Cell  | Content Cell
Content Cell  | Content Cell

* The mean of the sample is `r mean(pull(df, num_var))`. 
* The median of the sample is `r median(pull(df, num_var))`.
* The standard deviation of the sample is `r sd(pull(df, num_var))`.
